Data Structures Comparative Review Thing

### 2014-04-14 paper/paper.tex
Made a bunch of notes about implementation issues.

    \begin{abstract}
        We did research and got results.
    \end{abstract}

@@

>>>>

    \begin{abstract}
        We did research and got results~\cite{CallOfCthulhu}.
    \end{abstract}

@@

    \subsection{Possible errors caused by the implementation being not entirely perfect}

    We really did our best to make sure these kinds of things didn't happen.  However, there were
    still a number of measurements that do not follow from the underlying theory and are likely a
    consequence of the hardware involved.

    In particular, constructing a small hash table after constructing many big ones takes an
    absurdly long time.  Only the first hash table is affected, and the time is comparable to the
    time required to construct a 4k element hash table, which is just silly.  It probably has
    something to do with the allocator but the reason for such behaviour is still unclear.  The fact
    a hashtable needs contiguous memory probably has something to do with it, as well as the
    allocator returning memory to the operating system.  Still, the latter should also have happened
    with the other structures.  Bizarre.

    A similar issue occurs around 4k or 8k (depending on data structure).  In all three cases, the
    cost of insertion and querying grows at a higher rate than previously.  This is difficult to
    quantify\footnote{Can we do some sort of linear regression to prove this is the case?}, but it
    seems like some extra costs are added around then.  We suspect it is related either to the
    allocator having to get more memory or the CPU cache running out and more cache misses occuring.
    We'd measure that too if we had more time/resources.

    A possibly related issue is that the standard deviation of our measurements rises around that
    point.  That strengthens the possibility of it being allocator-related, as that would involve a
    system call and could cause scheduling issues (despite the system being otherwise very close to
    idle).
